Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-29 lloveras_2020_Albert_Section4_CON-TestHipotesis-Error2-V1.tex
..

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are {analysed} in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the {current} capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process. We should refer to minima in particular. We should mention the instruments and missions we use as data for DEMT, and define their accronyms too. Also, a couple of paragraphs on the AWSoM model and the SWMF, including references and defining the accronyms in the process.}

\albert{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona. The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM), a measure of the temperature distribution of the plasma contained in each voxel of the tomographic grid. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.

@@

\noindent 
\albert{being the} average relative difference between the tomographic and the synthetic FBEs. The final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}

%\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

@@

\noindent\notebyalbert{This section will summarize the AWSoM model. After a first version is written we will surely require some input from the Michigan friends. Points to cover:
\begin{itemize}
  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
  \item Explain the artificially extended TR. One paragraph.
  \item What are the products of the model we care about in this paper. One paragraph.
\end{itemize}
}

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\noindent\notebyalbert{El párrafo que sigue describe un algoritmo para identificar y seleccionar piernas up/down. Es correcta la jerga de "confidence level'' y el como se describe chi-squared test? Están bien mencionadas ambas cosas? Por ejemplo: confidence-level y conficence-interval, son dos cosas diferentes. Otro tema es: si entiendo bien el chi-squared utiliza los errores, correcto? Noten que modifiqué a errores porcentuales (mucho más claro) tal como se describen en las conclusiones (los corregí un poco, aquí y allá), que los saqué de la Tabla 7, y re-escribí toda la frase (ver nuevo texto naranja), es correcta?. Ahora bien, son errores muy pequeños para cada celda, es poner demasiada fé en la tomografía :) Estos son los errores del valor mediano de $\Tm$. Podemos discutirlo, pero creo que los errores por punto (es decir, la $\Tm$ de cada voxel) deben adjudicarse valores mayores. Quizá esto de paso hace que el chi-squared ralee menos?}

{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. \albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$.} In summary, to be selected a leg must meet all three following conditions:}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the \albert{$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.

@@

{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208. In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy. Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, {reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is quite uniform and artificially low}. As it turns out, around and above height this height the score $R$ is lower and the temperature results are more reliable. As a result, the temperature gradient along these legs is artificially larger, with the linear fit trying to simultaneously fit the artificially low values of $\Tm$ at lower heights. In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis. We will return to this point in the conclusion section.}

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   {\bf 7}&{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$}.

>>>>

\begin{abstract}
Observational {techniques} play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data {for} three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, {key to improve} their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations {using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and \albert{the declining} phase of \albert{SC 24 }. \albert{The 3D tomographic and MHD models} are analysed and compared in distinct coronal magnetic \albert{structures.} \notebyalbert{Aquí faltan dos frases de conclusiones a escribir cuando esté hecha la Section 4.}

@@

\noindent\albert{Diego: Esta nota en azul que sigue está modificada, inlcuíla así en la versión que mandes a Michigan, y borrá esta frase naranja :)}

\noindent\notebyalbert{Here we will put in a couple of paragraphs summarizing what SRT and DEMT are, including references and defining the accronyms in the process. We should refer to minima in particular. We should mention the instruments and missions we use as data for DEMT, and define their accronyms too. Also one paragraph on the SWMF/AWSoM model, including references and defining the accronyms on the way.}

\albert{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona. The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated \albert{in black color in the latitude-longitude (Carrington) maps of DEMT} reults in Section \ref{resu}.

@@

\noindent 
\albert{being the} average relative difference between the tomographic and the synthetic FBEs. \albert{The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\

@@

\noindent\albert{Diego: Esta nota en azul que sigue está modificada, inlcuíla así en la versión que mandes a Michigan, y borrá esta frase naranja :)}

\noindent\notebyalbert{This section will summarize the AWSoM model. Chip, Nishtha, do you think you could provide 2 or 3 paragraphs? We believe the points to cover are:
\begin{itemize}
  \item Data input. Link with the data input for DEMT in terms of dates, etc. One paragraph.
  \item Main physical and technical aspects (grid in particular) of the model.  One paragraph. 
  \item Explain the artificially extended TR. One paragraph.
  \item What are the products of the model we care about in this paper ($N_e$, $T_e$, $B$, $V$, as of now). One paragraph.
\end{itemize}
}

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and \albert{considering time-averaged heating rates.}

\noindent
\notebyalbert{Modifiqué la descripción del test estadístico en el próximo párrafo . Estuve leyendo un poco y hay que asegurarse que esto quede escrito bien. Yo busqué la frase más vaga que me parece tiene un sentido científico claro. Aquí hay una versión de divulgación:\\
{\tt www.statisticshowto.datasciencecentral.com/confidence-level/}\\
pero tener cuidado con esto: busquen ``Statistical Significance" en la Wikipedia, y lea la breve sección ``Redefining significance" al final del artículo.}

\albert{To determine if the leg of a traced field line is} of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature \albert{is significantly correlated with height} by requiring $|\rhoTr| > 0.5$. \albert{To test the goodness of the fit to the temperature-height data we perform a chi-squared test \citep{recipes} considering the uncertainty of the DEMT data points, selecting legs for which the fit matches the data with a 90\% confidence level.} In this way, legs for which the DEMT temperature does not show a significant \albert{correlation} with height, or the linear fit to temperature is \albert{not} good enough, are \albert{excluded from the} analysis. \albert{The test is also applied to the density-height data points, to ensure the trend is reasonably represented by the exponential fit.} Finally, selected legs are then classified as up or down according to if $\dr\Tm > 0$ or $\dr\Tm < 0$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. \albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$.} In summary, to be selected a leg must meet all three following conditions:}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the \albert{$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. \notebyalbert{Posiblemente quieras actualizar estos números.}

@@

\albert{The single notable difference between both rotations is to be found in the histograms for legs of type III in the open region. For those, the characteristic value is ${\rm Md}\left(\dr\Tm\right)\approx {\bf +X.X}$ and ${\bf Y.Y}\,\MK/\mrsun$ for CR-2208 and CR-2082, respectively}. This is related to the much larger $R$ score for the DEMT results along CH legs for CR-2208. In this case, DEMT performs poorly in modeling a LDEM that predicts the tomographic FBEs with reasonable accuracy. Indeed, visual inspection of the DEMT temperature maps for CR-2208 in Figure \ref{momento2}, reveals that in most of the CH region the result for $\Tm$ below height $1.105\,\mrsun$ is \albert{artificially uniform and low. Such results, mostly excluded of the analysis by the selection algorithm explained in Section \ref{trace}, imply the presence of some artificially large radial gradients of the DEMT temperature.} In general, the DEMT results in the CH region based on AIA data are thus much less reliable than in the rest of the analysis. We will return to this point in the conclusion section.

@@

\begin{table}[h!]
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
0    & 1&24 &(\Mi&19\%)  &   {\bf 7}&{\bf 1} &(\Pl&~3\%) &   1&09 &(\Pl&24\%) \\
I    & 1&15 &(\Mi&10\%)  &   7&5 &(\Pl&29\%) &   1&25 &(\Pl&24\%) \\
II   & 0&98 &(\Mi&20\%)  &   9&9 &(\Pl&19\%) &   1&36 &(\Pl&16\%) \\
III  & 0&65 &(\Mi&15\%)  &   7&6 &(\Pl&12\%) &   0&97 &(\Pl&~7\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.\notebyalbert{Notá que tenés un número en NEGRITA, y en la Tabla 2 tenés 3. Esos son números que yo había corregido, destacando en naranje y negrita, sacales la negrita. Quizá hay actualización de números para los Type III?}}
\label{tabla_demt}
\end{table}

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.
